---
title: "p8105_hw5_nl2655"
author: "Nankun"
date: "2019/11/11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(readr)
set.seed(10)
```

# Raw iris data

```{r}
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

# Replacing missing

```{r}
no_missing = function(x) {
  
  if (is.numeric(x)) {
    x = replace(x, is.na(x), round(mean(x, na.rm=TRUE), digits = 1))
  }
  else if (!is.numeric(x)) {
    x = replace(x, is.na(x), "virginica")
  } 
  
}
iris_no_na =
map(iris_with_missing, no_missing) %>% 
as.data.frame()
iris_no_na
```

# plot on longitudinal study

```{r}
read_csv = function(x) {
   read.csv(x)
}
z_df =
  tibble(list.files("./z")) %>% 
  rename(id = `list.files("./z")`) %>% 
  mutate(
    root = "./z/", 
    path = str_c(root, id) ,
    data = map(path, read_csv)
    ) %>% 
   mutate(
     id = str_replace(id, ".csv", ""),
     ) %>% 
  select(id, data) %>% 
  unnest() %>% 
   pivot_longer(
    week_1:week_8,
    names_to = "weeks",
    names_prefix = "week_",
    values_to = "result")

z_df %>% 
  ggplot(aes(x = weeks, y = result)) +
  geom_point(aes(group=id,color=id)) +
  geom_line(aes(group=id,color=id)) +
  labs(
    x="Weeks",
    y="Result",
    title = "longitudinal study rusult"
  )+
  theme(legend.position = "bottom")
```

# simulation

## association

```{r}
sim_regression = function(n = 30, beta0 = 2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  tibble(
    beta1_hat = round(coef(ls_fit)[2],digits = 4),
    p = round(broom::tidy(ls_fit)[[2,5]], digits = 4)
  )
  
}


sim_curr = 
  tibble(beta1 = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  mutate(
    significant = case_when(
    p > 0.05 ~ "nonsign",
    p <= 0.05 ~ "sign")
  )
sim_curr %>% 
  group_by(beta1, significant) %>% 
  summarize(
    n = n()
  ) %>% 
   pivot_wider(
    names_from = significant,
    values_from = n
 ) %>% 
  mutate(
    power = round(sign / (sign + nonsign), digits=4)
  ) %>% 
  ggplot(aes(x = beta1, y = power)) +
  geom_histogram(stat = "identity") +
  labs(
    x="Effect size",
    y="Power",
    title = "Association between effect size and power"
  )
```

From the plot we can see that on average, the larger the effect size is the larger the power will be.

## beta1 and hat

```{r}
sim_curr %>% 
  filter(significant == "sign") %>% 
  group_by(beta1) %>% 
  summarize(
    ave = mean(beta1_hat)
  ) %>% 
  ggplot(aes(x = beta1, y = ave)) + 
  geom_point(color = "blue") +
  geom_smooth(se = FALSE) +
  geom_point(aes(x = beta1, y = beta1, color = "pink")) +
  geom_smooth(aes(x = beta1, y = beta1, color = "pink")) +
   labs(
    x="Effect size",
    y="Value",
    title="Average Estimates of Beta1 Among Rejected compared to Beta1"
   ) +
  theme(legend.position = "hide")
```

The blue line is the average estimate beta1 hat by Effect size.

the orange line is the true value beta1 by Effect size.

From the plot, we can see that the average estimate beta1 always larger than the true value beta1(e.g. when beta1 = 1, two lines are obverisly different). Therefore, average of beta1 across tests for which the null is rejected is not equal to the true value of beta1.